---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE
)
```

# covid19usa

<!-- badges: start -->
<!-- badges: end -->

The goal of **covid19usa** is to embed the previously created shiny application for exploring COVID-19 data in the United States of America (USA) from assessment 2 within a package, and to refactor various parts of the application logic into R functions exported by the package. This is done in accordance with the assessment 3 instructions for ETC5523.

## Shiny application
As stated above, the shiny application was created as part of a previous assessment using the R package, shiny, to allow users to explore COVID-19 related data in the continental United States of America. For both the total number of cases and total number of deaths, the following data visualisations are provided:

1. A choropleth map displaying the spatial distribution of the total number of cases and deaths respectively, recorded at the state level.  
2. A timseries chart displaying the change in total cases and deaths recorded at the state level between the 22nd of January and the 28th of September of 2020, compared to the national average number of cases and deaths respectively.  
3. An accompanying table recording the exact number of cases and deaths recorded at the state level, and the national average, over the same time frame.  

For more information on the application itself and the data contained within it, please click [here](https://github.com/etc5523-2020/shiny-assessment-ltmoo2).

## Installation

<!-- You can install the released version of covid19usa from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("covid19usa") -->
<!-- ``` -->

The development version of covid19usa can be installed directly from [GitHub](https://github.com/etc5523-2020/r-package-assessment-ltmoo2) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-ltmoo2")
```
## Getting started

The application can then be launched using the following code:

```{r launch, eval=FALSE}
library(covid19usa)

launch_app()
```

## Package functions
The four functions below were created in order to improve logic of the aforementioned shiny application. The first function, `random_states` creates a vector of two randomly selected states names from a supplied data set, in this case `usa_state_map`.
```{r random}
set.seed(1)
library(covid19usa)

random_states(usa_state_map)
```
This function was created and implemented within the `create_input` function in order to automatically select two different US states for comparison each time the application is launched In this example, by default the application will display comparisons for `CALIFORNIA` and `SOUTH CAROLINA`. In addition, this function is used to create all adjustable inputs for the application.

```{r input, eval=FALSE}
create_input("state", usa_state_map)
```

Thirdly, on the server side, the function `average_measure` can be used to produce a summary count of either `tot_cases` or `tot_death` for COVID19 in the USA. This is used to construct the timeseries plot seen in the application.

```{r average}
library(dplyr)

example <- average_measure(usa_covid_data, "tot_cases") %>%
  arrange(-tot_cases) %>%
  head(5)

example
```
The final function, `present_table`, converts any data frame into a stylish and presentable table using the `kableExtra` package and can be seen alongside the timeseries chart in the application.

```{r present}
library(dplyr)

usa_covid_data %>%
  select(date, state, tot_cases)%>%
  filter(state == "colorado") %>%
present_table("cases", "Total cases in Colorado per day")
```

