---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covid19usa

<!-- badges: start -->
<!-- badges: end -->

The goal of covid19usa is to embed the previously created shiny application for exploring COVID19 data in the United States of America (USA) from assessment 2 within a package, and to refactor various parts of the application logic into R functions exported by the package. This is done in accordance with the assessment 3 instructions for ETC5523.

## Installation

<!-- You can install the released version of covid19usa from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("covid19usa") -->
<!-- ``` -->

The development version of covid19usa can be installed directly from [GitHub](https://github.com/etc5523-2020/r-package-assessment-ltmoo2) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-ltmoo2")
```
## Example

The application can be launched using the following code:

```{r example, eval=FALSE}
library(covid19usa)
launch_app()
```
