---
title: "Exploring COVID19 in the USA with Shiny"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exploring COVID19 in the USA with Shiny}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette is for the use of the `covid19usa` package, and describes how to launch the shiny application contained within the package, what the application itself can do, and guidelines for using and interpreting the visualisations contained within it.

## Loading covid19usa 
Before the application can be launched, the package itself must be loaded. This can be done directly from [GitHub](https://github.com/etc5523-2020/r-package-assessment-ltmoo2) with:

```{r install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-ltmoo2")
```

## Usage
Once the package is downloaded, the primary component of the package, the shiny application, can then be launched using the following `launch_app` function.
```{r launch, eval=FALSE}
library(covid19usa)
launch_app()
```

The application is an interactive web application that allows users to explore COVID-19 related data in the continental United States of America (USA) sourced from the [Centers for Disease Control and Prevention](https://data.cdc.gov/Case-Surveillance/United-States-COVID-19-Cases-and-Deaths-by-State-o/9mfq-cb36?fbclid=IwAR1QbXngfoMy1NE9vO-QSe40zfo11iApIqOr4Hb3EB6eMia7JSY2DncPF00) using shiny.  

Within the app, users can compare the total number of cases and deaths recorded by each of the states in the country using the three following data visualisations:   

1. A choropleth map displaying the spatial distribution of the total number of cases and deaths respectively, recorded at the state level.  
2. A timseries chart displaying the change in total cases and deaths recorded at the state level between the 22nd of January and the 28th of September of 2020, compared to the national average number of cases and deaths respectively.  
3.  An accompanying table recording the exact number of cases and deaths recorded at the state level, and the national average, over the same time frame.
